\documentclass[sigconf]{acmart}
\settopmatter{printfolios=true,printccs=false,printacmref=false,authorsperrow=5}
%\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)
\usepackage{color}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{url}
\usepackage{multicol}
\usepackage{booktabs} % For formal tables
\usepackage{times}

\setcopyright{none}


%\acmConference{Submitted to SIGIR}{2018}{} 
%\acmYear{2018}


\begin{document}

\newcommand{\alg}{Sparta}  
\newcommand{\inred}[1]{{\color{red}{#1}}}
\newcommand{\inblue}[1]{{\color{blue}{#1}}}
\newcommand{\remove}[1]{}

% ****************** TITLE ****************************************

\title{Fast Parallel Top-K Retrieval of Verbose Queries}


\author{Gali Sheffi}
\affiliation{Yahoo! Research}

\author{Dmitry Basin}
\affiliation{Yahoo! Research}

\author{Edward Bortnikov}
\affiliation{Yahoo! Research\thanks{*Work done while at Yahoo! Research}}

\author{David Carmel}
\affiliation{Amazon\footnote{Work done while at Yahoo! Research}}

\author{Idit Keidar}
\affiliation{Yahoo! Research \\ and Technion}


% Gali Sheffi\\
%        \affaddr{Yahoo! Research}\\
%        \email{gsheffi@yahoo-inc.com}
% Dmitry Basin\\
%        \affaddr{Yahoo! Research}\\
%        \email{dbasin@yahoo-inc.com}
% Edward Bortnikov\\
%        \affaddr{Yahoo! Research}\\
%        \email{ebortnik@yahoo-inc.com}\\
% David Carmel\\
%        \affaddr{Yahoo! Research}\\
%        \email{dcarmel@yahoo-inc.com}
% Idit Keidar\\
%        \affaddr{Technion and Yahoo! Research}\\
%       \email{idish@yahoo-inc.com}



\begin{abstract}
Top-k document retrieval is emerging as a performance bottleneck in query processing as verbose queries are becoming 
mainstream, while state-of-the-art algorithms fail to process such long queries in real time. To date, attempts to
accelerate top-k evaluation 
via approximate result computation and intra-query parallelism have produced limited results. 

We present \alg\ -- a practical parallel algorithm that exploits multi-core hardware to run approximate top-k retrieval 
within interactive latency bounds. Its design is inspired by  Fagin et al.'s seminal Threshold Algorithm for  aggregation in databases. 
\alg\ scales through lightweight coordination and context sharing among concurrent threads. The resulting algorithm 
is highly scalable in the number of query terms. For example, when applied to the 50M-document public ClueWeb09B 
dataset, \alg\  processes $12$-term queries $3.6$ times faster than the state-of-the-art. 
\end{abstract}

\maketitle
\input{macros}

\input{intro}
\input{Background}
\input{algorithm}
\input{evaluation}
\input{related}
%\input{conclusions}


\bibliographystyle{ACM-Reference-Format}
\bibliography{references}  


\end{document}
