\documentclass[runningheads]{llncs}


\usepackage{color}
% \usepackage{subcaption}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{url}
\usepackage{multicol}
\usepackage{booktabs} % For formal tables
\usepackage{times}

%\setcopyright{none}
%\acmConference{Submitted to SIGIR}{2018}{} 
%\acmYear{2018}

\usepackage{multicol}
\input{macros}

\newcommand{\alg}{Sparta}  
\newcommand{\inred}[1]{{\color{red}{#1}}}
\newcommand{\inblue}[1]{{\color{blue}{#1}}}
\newcommand{\remove}[1]{}
\newcommand{\bigdataset}[1]{} % remove for now, add later

\begin{document}

% ****************** TITLE ****************************************

\title{Fast Parallel Top-K Retrieval of Verbose Queries}

\author{Gali Sheffi\inst{1,2}\and %{Yahoo Research, Oath}{gsheffi@oath.com}{}{}
Dmitry Basin\inst{1}\and %{Yahoo Research, Oath}{dbasin@oath.com}{}{}
Edward Bortnikov\inst{1}\and %{Yahoo Research, Oath}{ebortnik@oath.com}{}{}
David Carmel\inst{3}\and %{Amazon}{david.carmel@gmail.com}{}{}
Idit Keidar\inst{1,2} %{Technion and Yahoo Research, Oath}{idish@ee.technion.ac.il}{}{}
}

\authorrunning{G. Sheffi et al.}

\institute{Yahoo Research \and Technion \and Amazon
%\email{lncs@springer.com}\\
%\url{http://www.springer.com/gp/computer-science/lncs} 
}
\maketitle




\begin{abstract}
Top-k document retrieval is emerging as a performance bottleneck in query processing as verbose queries are becoming 
mainstream, while state-of-the-art algorithms fail to process such long queries in real time. To date, attempts to
accelerate top-k evaluation 
via approximate result computation and intra-query parallelism have produced limited results. 

We present \alg\ -- a practical parallel algorithm that exploits multi-core hardware to run approximate top-k retrieval 
within interactive latency bounds. Its design is inspired by  Fagin et al.'s seminal Threshold Algorithm for  aggregation in databases. 
\alg\ scales through lightweight coordination and context sharing among concurrent threads. The resulting algorithm 
is highly scalable.
\bigdataset{ 
both in the number of query terms and in the searched index size. 
}
%For example, 
When applied to the 50M-document public ClueWeb09B 
dataset, \alg\  processes $12$-term queries $3.6$ times faster than the state-of-the-art. 
\bigdataset{
On a tenfold  bigger index, 
\alg\ continues to process queries at the same speed, whereas today's best-in-class algorithm is more than 60 times slower. 
}
\alg\ further significantly improves throughput.% on production-motivated query mixes. 

\keywords{Parallel computing, web-search, top-k}
\end{abstract}

\input{intro}
\input{Background}
\input{algorithm}
\input{evaluation}
\input{related}
\input{conclusions}

\bibliographystyle{splncs04}

\bibliography{references}  


\end{document}
